---
title: "My sample mean"
author: "Patrick Heinze"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{My_sample_mean}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Overview
The goal of My sample mean is to provide a function to calculate the sample mean of a vector

## Installation

You can install PatrickMean from github with:

```{r gh-installation, eval = FALSE, echo = TRUE}
# install.packages("devtools")
devtools::install_github("PatrickH91/PatrickMean")
```

## Usage

```{r setup}
library(PatrickMean)
```


## Create some data

First we will check that sample mean gives correct value by calculating the sample mean for the numbers 1 to 10. 

```{r}
x  <- 1:10
```

## Using the `my_mean()` function

The `my_mean()` function will take a numeric vector

$$
x_1, x_2, \ldots, x_n
$$

and return the sample mean:

$$
\bar{x} = \frac1n \sum^n_{i = 1}x_i
$$

```{r}
my_mean(x)
```

We can check this is correct with 

$$
\bar x = \frac{1}{10}(1 + 2 + \ldots + 10) = \frac{1}{10}\times \frac{11\times10}{2} = 5.5.
$$



